% Tailored CV for Dataiku - Fullstack Software Engineer, Core
% Replace contact placeholders before sending.
\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.25in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.18in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ghislain THEUBO} \\ \vspace{2pt}
    \small Paris, France $|$ +33 6 82 86 62 79 $|$
    \href{mailto:TODO@email.com}{TODO@email.com} $|$
    \href{https://www.linkedin.com/in/TODO}{linkedin.com/in/TODO} $|$
    \href{https://github.com/TODO}{github.com/TODO}
\end{center}

\vspace{-8pt}
\begin{center}
    \textbf{Full-Stack Software Engineer -- AI/Data Products -- Python, TypeScript, PostgreSQL, Docker}
\end{center}
\vspace{-8pt}

\section{Profile}
\small{
Recent Ensimag software engineer with hands-on experience building a real full-stack AI/data product: structured clinical data workflows, backend APIs, PostgreSQL persistence, LLM integration, streaming, tests and CI. Strong alignment with Dataiku Core: stack-agnostic engineer, comfortable moving between backend performance, data modeling, product UX and platform reliability. Particularly interested in data preparation, AI features, MLOps and scalable tools that help technical and non-technical users build with data.
}

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Grenoble INP - Ensimag}{Grenoble, France}
    {Engineering degree in Computer Science / Software Engineering}{Graduated 2025}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {ARCANE -- Clinical Data and AI Decision-Support Platform}{Paris, France}
    {Full-Stack / AI Software Engineer}{2024 -- 2025}
    \resumeItemListStart
      \resumeItem{Built an end-to-end product combining \textbf{React/TypeScript} frontend workflows, \textbf{Python/FastAPI} backend APIs and \textbf{PostgreSQL} data persistence for structured clinical records.}
      \resumeItem{Designed and implemented data-heavy workflows: patient search/filtering, JSON import, clinical record views, profile persistence, schema versioning and backend/frontend validation.}
      \resumeItem{Created API layers for authentication, patients, administration, clinical data and ARGOS AI discussions; used explicit services/use cases to keep business logic testable.}
      \resumeItem{Integrated LLM features with provider abstraction: disabled/mock/openai-compatible modes, server-side credential handling, JSON report generation and Server-Sent Events streaming.}
      \resumeItem{Improved backend maintainability through layered architecture, dependency injection, repository boundaries, typed Pydantic models and application-level error handling.}
      \resumeItem{Managed database evolution with Alembic migrations, SQL scripts, PostgreSQL JSONB fields and compatibility paths for legacy payloads.}
      \resumeItem{Set up and maintained quality gates: Vitest/Testing Library, Pytest/FastAPI tests, typecheck, build, Alembic migration smoke tests and GitHub Actions CI.}
    \resumeItemListEnd

  \resumeSubheading
    {Engineering internships and applied software projects}{France}
    {Backend / Full-Stack Software Engineering}{2022 -- 2024}
    \resumeItemListStart
      \resumeItem{Delivered software modules using \textbf{Python}, \textbf{Java}, \textbf{C\#} and \textbf{TypeScript}; strong foundation in algorithms, OOP, API design and relational databases.}
      \resumeItem{Worked in Git-based team environments, reading existing code, shipping incremental changes and documenting technical decisions for maintainability.}
      \resumeItem{Built habits relevant to platform teams: clear abstractions, tests close to behavior, pragmatic debugging and clean handover documentation.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Selected Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{AI Report and Assistant Workflows} $|$ \emph{FastAPI, LLM APIs, SSE, React, TypeScript}}{}
    \resumeItemListStart
      \resumeItem{Implemented a backend-controlled AI workflow that can generate structured JSON reports and stream assistant responses while remaining testable without external network calls.}
      \resumeItem{Separated AI ports from application use cases to support multiple providers and deterministic CI-friendly mocks.}
    \resumeItemListEnd
  \resumeProjectHeading
    {\textbf{Data Persistence and Validation} $|$ \emph{PostgreSQL, Alembic, SQL, JSONB, Zod}}{}
    \resumeItemListStart
      \resumeItem{Built versioned patient-profile persistence with schema migration rules, optimistic conflict handling and consistent validation across API and UI boundaries.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Backend / Platform}{: Python, FastAPI, REST APIs, Pydantic, Java/OOP fundamentals, C\#, API design, service architecture} \\
    \textbf{Frontend}{: React, TypeScript, Vite, Tailwind, shadcn/ui, React Query, component testing, Angular fundamentals} \\
    \textbf{Data / AI}{: PostgreSQL, SQL, Alembic, JSONB, data validation, LLM APIs, RAG concepts, structured outputs, SSE streaming} \\
    \textbf{Cloud / DevOps}{: Docker, GitHub Actions, CI/CD, Linux, Azure fundamentals, deployment configuration, observability mindset} \\
    \textbf{Quality}{: Pytest, Vitest, Testing Library, typechecking, migration tests, code review, clean architecture}
  }}
\end{itemize}

\section{Languages}
\small{French: fluent \quad English: professional working proficiency}

\end{document}
